data_cleaning_longer_period

### 2024-08-26 code/manuscript_data_cleaning.Rmd
larger data file, more detailed analysis, new temp files

included.years <- 2010:2021
included.treat <- 2013:2021

@@

## Zips
locs <- paste("/Users/jhm65/Dropbox/Git/UDS/UDS-", c(2012:2021), "-Full-Dataset.xlsx", sep = "")
uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")[,c(1:4, 6, 5)]

@@

uds.zip

@@

## Sites
locs <- paste("/Users/jhm65/Dropbox/Git/UDS/UDS-", c(2012:2021), "-Full-Dataset.xlsx", sep = "")

@@

for(i in 4:(length(locs)-1)){
  uds.sites <- rbind(uds.sites, read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
                       select("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code") %>% 
  mutate(Year = 2011 + i))
}

temp.sites <- read_excel(locs[i+1], sheet = "HealthCenterSiteInfo" )%>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2021)
colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

@@

uds.sites.old <- read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Sites.csv", colClasses = "character") %>% 
  mutate(Year = as.numeric(Year))

@@

#write.csv(x = uds.sites.full, file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Sites96to21.csv")

@@

for (g in 1:13){
  g
coded <- rbind(coded, 
               geo(street = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site Street Address`, 
             city = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site City`, 
             state = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )
}

coded <- rbind(coded, 
               geo(street = tbcoded[c(14001:14253),]$`Site Street Address`, 
             city = tbcoded[c(14001:14253),]$`Site City`, 
             state = tbcoded[c(14001:14253),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )

@@

chc <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_raw/chc.csv")

@@

for (i in 1:10){
  census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
                       variables = c("B01003_001","B17001_001","B17001_002","B01001_002","B01001_026",
                                     "B02001_002","B02001_003","B02001_004","B02001_005","B02001_006","B02001_008",
                                     "B03001_003", 
                                     "B01001_003","B01001_004","B01001_005","B01001_006","B01001_007","B01001_008","B01001_009",
                                     "B01001_010","B01001_011","B01001_013","B01001_014","B01001_015","B01001_016","B01001_017",
                                     "B01001_018","B01001_019","B01001_020","B01001_021","B01001_022","B01001_023","B01001_024","B01001_025",
                                     "B01001_027","B01001_028","B01001_029","B01001_030","B01001_031","B01001_032","B01001_033","B01001_034",
                                     "B01001_035","B01001_036","B01001_037","B01001_038","B01001_039","B01001_040","B01001_041","B01001_042","B01001_043",
                                     "B01001_044","B01001_045","B01001_046","B01001_047","B01001_048","B01001_049",
                                     "B06009_002","B06009_003", "B06009_004","B06009_005","B06009_006",
                                     "B23025_002","B23025_005",
                                     "C27007_001", "C27007_004", "C27007_007", "C27007_010", "C27007_014", "C27007_017", "C27007_020",
                                     "B18135_001","B18135_007","B18135_012","B18135_018","B18135_023","B18135_029","B18135_034"), 
                       year = 2011 + i) %>% 
  pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
    mutate(YEAR = 2011 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
           AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
           Age18to64 = B01001_007 + B01001_008 + B01001_009 + B01001_010 + B01001_011 + B01001_013 + B01001_014 + B01001_015 + 
                       B01001_016 + B01001_017 + B01001_018 + B01001_019 + B01001_031 + B01001_032 + B01001_033 + B01001_034 +
                       B01001_035 + B01001_036 + B01001_037 + B01001_038 + B01001_039 + B01001_040 + B01001_041 + B01001_042 + B01001_043, 
           Age65andOver = B01001_020 + B01001_021 + B01001_022 + B01001_023 + B01001_024 + B01001_025 + 
                          B01001_044 + B01001_045 + B01001_046 + B01001_047 + B01001_048 + B01001_049, 
           Male = B01001_002, Female = B01001_026, 
           White = B02001_002, Black = B02001_003, AIAN = B02001_004, Asian = B02001_005 + B02001_006, MR = B02001_008, 
           Hispanic = B03001_003, 
           EducLow = B06009_002, EducMid = B06009_003 + B06009_004, EducHigh = B06009_005 + B06009_006,
           Unemployed = B23025_005, Unemp_denom = B23025_002,
           MCD.denom = C27007_001	, Medicaid = C27007_004	 + C27007_007 + C27007_010	+ C27007_014 + C27007_017 + C27007_020,
           Unins.denom = B18135_001, Uninsured = B18135_007 + B18135_012 + B18135_018 + B18135_023 + B18135_029 + B18135_034) %>% 
    select(ZipCode = GEOID, NAME, YEAR, TotalPop:Uninsured))

@@

census %>% 
  filter(YEAR == 2020) %>% 
  select(ZipCode) %>% 
  #unique() %>% 
  table() %>% 
  table()
```

## Merge with Older UDSs 1996-2011
```{r}
uds.cw <- read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_CW.csv", colClasses = "character") %>% 
  mutate(link.ID = ifelse(is.na(ModernGranteeID) & !is.na(LongGrantID) & Year != 2010, LongGrantID, 
                   ifelse(is.na(ModernGranteeID) & !is.na(GranteeID), GranteeID, BHCMIS.ID)), 
         Year = as.integer(Year))

uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(BHCMIS.ID == '010060' & Year %in% c(2007:2011)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA)

@@

uds.3B.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)

uds.3B.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

@@

                  cbind(Year = 2018, uds.3B.2018),
                  cbind(Year = 2019, uds.3B.2019), 
                  cbind(Year = 2020, uds.3B.2020),
                  cbind(Year = 2021, uds.3B.2021)) %>%

@@

uds.3B <- rbind(
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2007)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2008)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
    setNames(namevec),
    uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2009)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2010)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2011)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.3B)
uds.3B %>% 
  arrange(BHCMISID, Year)

# Table 4
uds.4.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb) 
uds.4.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)

>>>>

included.years <- 2010:2023
included.treat <- 2013:2023

@@

## Zips
locs <- paste("/Users/markow/Dropbox/Git/UDS/UDS-", c(2012:2023), "-Full-Dataset.xlsx", sep = "")
uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")[,c(1:4, 6, 5)]

@@

@@

## Sites
locs <- paste("/Users/markow/Dropbox/Git/UDS/UDS-", c(2012:2023), "-Full-Dataset.xlsx", sep = "")

@@

for(i in 4:(length(locs)-3)){
  uds.sites <- rbind(uds.sites, read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
                       select("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code") %>% 
  mutate(Year = 2011 + i))
}

## 2021
temp.sites <- read_excel(locs[i+1], sheet = "HealthCenterSiteInfo" )%>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2021)
colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

@@

## 2022
temp.sites <- read_excel(locs[i+2], sheet = "HealthCenterSiteInfo" )%>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2022)
colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

## 2023
temp.sites <- read_excel(locs[i+3], sheet = "HealthCenterSiteInfo" )%>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2023)
colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

uds.sites.old <- read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Sites.csv", colClasses = "character") %>% 
  mutate(Year = as.numeric(Year))

@@

#write.csv(x = uds.sites.full, file = "//Users/markow/Dropbox/Git/APMs/data_processed/Sites96to21.csv")

uds.sites %>% 
  filter(Year %in% c(2021, 2022, 2023)) %>% 
  arrange(`Grant Number`, Year)

@@

for (g in 1:16){
  g
coded <- rbind(coded, 
               geo(street = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site Street Address`, 
             city = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site City`, 
             state = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )
}

coded <- rbind(coded, 
               geo(street = tbcoded[c(17001:17152),]$`Site Street Address`, 
             city = tbcoded[c(17001:17152),]$`Site City`, 
             state = tbcoded[c(17001:17152),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )

@@

chc <- read.csv("//Users/markow/Dropbox/Git/Competition/data_raw/chc.csv")

@@

for (i in 1:11){
  census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
                       variables = c("B01003_001","B17001_001","B17001_002","B01001_002","B01001_026",
                                     "B02001_002","B02001_003","B02001_004","B02001_005","B02001_006","B02001_008",
                                     "B03001_003", 
                                     "B01001_003","B01001_004","B01001_005","B01001_006","B01001_007","B01001_008","B01001_009",
                                     "B01001_010","B01001_011","B01001_013","B01001_014","B01001_015","B01001_016","B01001_017",
                                     "B01001_018","B01001_019","B01001_020","B01001_021","B01001_022","B01001_023","B01001_024","B01001_025",
                                     "B01001_027","B01001_028","B01001_029","B01001_030","B01001_031","B01001_032","B01001_033","B01001_034",
                                     "B01001_035","B01001_036","B01001_037","B01001_038","B01001_039","B01001_040","B01001_041","B01001_042","B01001_043",
                                     "B01001_044","B01001_045","B01001_046","B01001_047","B01001_048","B01001_049",
                                     "B06009_002","B06009_003", "B06009_004","B06009_005","B06009_006",
                                     "B23025_002","B23025_005",
                                     "C27007_001", "C27007_004", "C27007_007", "C27007_010", "C27007_014", "C27007_017", "C27007_020",
                                     "B18135_001","B18135_007","B18135_012","B18135_018","B18135_023","B18135_029","B18135_034"), 
                       year = 2011 + i) %>% 
  pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
    mutate(YEAR = 2011 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
           AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
           Age18to64 = B01001_007 + B01001_008 + B01001_009 + B01001_010 + B01001_011 + B01001_013 + B01001_014 + B01001_015 + 
                       B01001_016 + B01001_017 + B01001_018 + B01001_019 + B01001_031 + B01001_032 + B01001_033 + B01001_034 +
                       B01001_035 + B01001_036 + B01001_037 + B01001_038 + B01001_039 + B01001_040 + B01001_041 + B01001_042 + B01001_043, 
           Age65andOver = B01001_020 + B01001_021 + B01001_022 + B01001_023 + B01001_024 + B01001_025 + 
                          B01001_044 + B01001_045 + B01001_046 + B01001_047 + B01001_048 + B01001_049, 
           Male = B01001_002, Female = B01001_026, 
           White = B02001_002, Black = B02001_003, AIAN = B02001_004, Asian = B02001_005 + B02001_006, MR = B02001_008, 
           Hispanic = B03001_003, 
           EducLow = B06009_002, EducMid = B06009_003 + B06009_004, EducHigh = B06009_005 + B06009_006,
           Unemployed = B23025_005, Unemp_denom = B23025_002,
           MCD.denom = C27007_001	, Medicaid = C27007_004	 + C27007_007 + C27007_010	+ C27007_014 + C27007_017 + C27007_020,
           Unins.denom = B18135_001, Uninsured = B18135_007 + B18135_012 + B18135_018 + B18135_023 + B18135_029 + B18135_034) %>% 
    select(ZipCode = GEOID, NAME, YEAR, TotalPop:Uninsured))

@@

census %>% 
  filter(YEAR == 2022) %>% 
  select(ZipCode) %>% 
  #unique() %>% 
  table() %>% 
  table()
```

## Merge with Older UDSs 1996-2011
```{r}
uds.cw <- read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_CW.csv", colClasses = "character") %>% 
  mutate(link.ID = ifelse(is.na(ModernGranteeID) & !is.na(LongGrantID) & Year != 2010, LongGrantID, 
                   ifelse(is.na(ModernGranteeID) & !is.na(GranteeID), GranteeID, BHCMIS.ID)), 
         Year = as.integer(Year))

uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(BHCMIS.ID == '010060' & Year %in% c(2007:2011)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA)

@@

uds.3B.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)

uds.3B.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

@@

                  cbind(Year = 2018, uds.3B.2018),
                  cbind(Year = 2019, uds.3B.2019), 
                  cbind(Year = 2020, uds.3B.2020),
                  cbind(Year = 2021, uds.3B.2021),

                  cbind(Year = 2022, uds.3B.2022),
                  cbind(Year = 2023, uds.3B.2023)) %>%

@@

uds.3B <- rbind(
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2007)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2008)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
    setNames(namevec),
    uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2009)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2010)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2011)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.3B)
uds.3B %>% 
  arrange(BHCMISID, Year)

# Table 4
uds.4.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb) 
uds.4.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
